---
title: "Formulae"
output: html_document
---
```{r,include=FALSE}
library(tidyverse)
library(lubridate)
```
## ISLR v2 Formulae List
$(1.1)$  
$\mbox{a vector of length p}$  
$x_i = \begin{pmatrix} x_{i1} \\ x_{i2} \\ … \\ x_{ip} \end{pmatrix}$  
```{r}
# ひとまず全部書き出し→一発検索可能状態
# その後、レイアウト整え
```

$(2.1)$  
$Y = f(x) + \varepsilon$  

$(2.2)$  
$\hat Y = \hat f(x)$  

$(2.3)$  
$E(Y-\hat Y)^2 = E[f(x)+\varepsilon-\hat f(x)]^2$
$=[f(x)-\hat f(x)]^2+Var(\varepsilon)$  
$\overbrace{Reducible}^{[f(x)-\hat f(x)]^2} \overbrace{Irreducible}^{+Var(\varepsilon)}$  
```{r}
# [f(x)-\hat f(x)]^2 : Reducible
# Var(\varepsilon)   : Irreducible
```

$(2.4)$  
$f(x)=\beta_0+\beta_1X_1+\beta_2X_2+…+\beta_pX_p$

$(2.5)$  
$MSE=\frac{1}{n}\sum_{i=1}^n(y_i-\hat f(x_i))^2$

$(2.6)$  
$Avg(y_0-\hat f(x_0))^2$

$(2.7)$  
$E(y_0-\hat f(x_0))^2$
$=Var(\hat f(x_0))+[Bias(\hat f(x_0))]^2+Var(\varepsilon)$

$(2.8)$  
$\frac{1}{n}\sum_{i=1}^nI(y_i\neq \hat y_i)$

$(2.9)$  
Test Error Rate:  
$Avg(I(y_0\neq \hat y_0))$

$(2.10)$  
Bayes Classifier  
$Pr(Y=j|X=x_0)$

$(2.11)$  
Bayes Error Rate  
$1-E(\underset{j}{max}Pr(Y=j|X))$

$(2.12)$  
KNN Classifier  
$Pr(Y=j|X=x_0)$  
$=\frac{1}{k}\sum_{i\in\mathcal{N}}I(y_i=j)$

## Linear Regression  
$(3.1)$  
$Y\approx \beta_0+\beta_1X$  

$(3.2)$
$\hat y = \hat \beta_0+\hat \beta_1x$  
$\mbox{Residual Sum of Squares}$  
$RSS=e_1^2+e_2^2+\cdots+e_n^2$  

$(3.3)$
$RSS=(y_1-\hat \beta_0-\hat \beta_1x_1)^2+(y_2-\hat \beta_0-\hat \beta_1x_2)^2+\cdots+(y_n-\hat \beta_0-\hat \beta_1x_n)^2$  

$(3.4)$
$\hat \beta_1=\frac{\sum_{i=1}^n(x_i-\bar x)(y_i-\bar y)}{\sum_{i=1}^n(x_i-\bar x)}$  
$\hat \beta_0=\bar y-\hat \beta_1 \bar x$  

$(3.5)$  
$Y=\beta_0+\beta_1X+\varepsilon$  

$(3.6)$  
$Y=2+3X+\varepsilon$  

$(3.7)$  
$Var(\hat \mu)=SE(\hat \mu)^2=\frac{\sigma^2}{n}$

$(3.8)$  
$SE(\hat\beta_0)^2=\sigma^2[\frac{1}{n}+\frac{\bar x^2}{\sum_{i=1}^n(x_i-\bar x)^2}]$,  $SE(\hat\beta_1)^2=\frac{\sigma^2}{\sum_{i=1}^n(x_i-\bar x)^2}$  

$(3.9)$  
$\hat\beta_1\pm2\cdot SE(\hat\beta_1)$  

$(3.10)$  
$[\hat\beta_1-2\cdot SE(\hat\beta_1),\hat\beta_1+2\cdot SE(\hat\beta_1)]$  

$(3.11)$  
$\hat\beta_0\pm2\cdot SE(\hat\beta_0)$  

$(3.12)$ 
$\mbox{The }\textit{null hypothesis}$
$H_0:\mbox{There is no relationship between X and Y}$  

$(3.13)$  
$\mbox{The }\textit{alternative hypothesis}$
$H_a:\mbox{There is some relationship between X and Y}$

$(3.14)$
$t=\frac{\hat\beta_1-0}{SE(\hat\beta_1)},$

options(knitr.table.format = "latex")
$$
\begin{table}[h]
  \caption{TABLE 3.1}
  \centering
    \begin{tabular}{rllll}
      \hline
       & Coefficient & Std.error & t-statistic & p-value \\
      Intercept & 7.0325 & 0.4578 & 15.36 & <0.0001 \\
      TV & 0.0475 & 0.0027 & 17.64 & <0.0001 \\
      \hline
    \end{tabular}
  \end{table}
$$
$$The table is numbered \ref{ex:table}
\end{document}$$